decompr: GVC decomposition in R

### 2015-01-29 draft.Rnw
line breaks and move tables 1 and 2
update to cleveref (cref)

As can be seen above, a \textbf{decompr} class object is in fact a list containing thirty different objects.
Depending on the choice of decomposition, all or some of these objects are used

@@

\subsection{Output}
We can now analyse the output which consists of a GNxGN matrix that gives for each country and industry the
value added origins of its exports by country and industry. To this end, we look at the results of the Leontief
decomposition for our example data set (Table \ref{tab:leon}). In the first column we find the source countries and
industries while the first row contains the using countries and industries. The first element, $28.52$, thus gives the
amount of value added that the Argentinian Agriculture industry has contributed to the exports of the Argentinian
Agriculture industry. Similarly, the last element of this row, $4.12$, gives the amount of value added that the
Argentinian Agriculture industry has contributed to the exports of the German Transport Equipment industry.

A key advantage of the decomposition becomes clear when we compare the decomposed values with the intermediate trade
values of the non-decomposed IO table when multiplied with the exports over output ratio to create
comparability (Table \ref{tab:noleon}). We see for instance that Argentina's Agriculture industry
contributes significantly more value added to the German Transport Equipment industry than suggested
by the non-decomposed IO table. The reason is that Argentina's Agriculture industry is an important supplier
to Turkey's Textile and Leather industry which is in turn an important supplier for the German Transport
Equipment industry. The decomposition thus allows us to see how the value added flows along this Global Value Chain.

@@

\begin{table}[htbp]

\scriptsize

@@

Table \ref{tab:wwz} shows the results for the example data. The first column lists exporter, exporting industry, and direct importer. Note that the value added is domestic but not necessarily created in the exporting industry. When exporter and importer are identical, the values are zero since there are no exports. The first row lists the 16 components of bilateral exports at the sector level and three checksums.

The first eight components relate to domestic value added of the exporting country contained in the sectoral exports of the exporting industry to the direct importer. For instance, the first non-zero element in Table \ref{tab:wwz} refers to $DVA\_FIN$ or domestic value added in final good exports. It shows that there are 5.47 units of domestic value added in the exports of final goods from Argentina's Agriculture industry to Turkey. In the same row the third term,  $DVA\_INTrexI1$, is slightly more complicated. As mentioned above it gives the amount of domestic Value added in intermediate exports re-exported to third countries as intermediate goods to produce domestic final goods. In our example this means that there are 1.14 units of domestic value added in the intermediate exports of Argentina's Agriculture industry to Turkey that are re-exported by Turkey as intermediates to a third country which produces final goods with it. Terms six to eight concern domestic value added that eventually returns home. $RDV\_FIN2$ reveals for example that there are 0.35 units of domestic value added in the intermediate exports of Argentina's Agriculture industry to Turkey that Turkey re-exports as intermediates to Argentina for the latter's final good production.

>>>>

As can be seen above, a \textbf{decompr} class object is in fact a list containing thirty different objects.
Depending on the choice of decomposition, all or some of these objects are used.

\begin{landscape}
\begin{table}[htbp]
\scriptsize

\end{table}
\end{landscape}

@@

\subsection{Output}
We can now analyse the output of the Leontief decomposition, which consists of a GNxGN matrix that gives for each country and industry the
value added origins of its exports by country and industry.
To this end, we look at the results of the Leontief decomposition for our example data set (\cref{tab:leon}).
In the first column we find the source countries and industries while the first row contains the using countries and industries.
The first element, $28.52$, thus gives the amount of value added that the Argentinian Agriculture industry has contributed to the exports of the Argentinian Agriculture industry.
Similarly, the last element of this row, $4.12$, gives the amount of value added that the Argentinian Agriculture industry has contributed to the exports of the German Transport Equipment industry.

A key advantage of the decomposition becomes clear when we compare the decomposed values with the intermediate trade
values of the non-decomposed IO table when multiplied with the exports over output ratio to create
comparability (\cref{tab:noleon}).
We see for instance that Argentina's Agriculture industry contributes significantly more value added to the German Transport Equipment industry than suggested by the non-decomposed IO table.
The reason is that Argentina's Agriculture industry is an important supplier to Turkey's Textile and Leather industry which is in turn an important supplier for the German Transport Equipment industry.
The decomposition thus allows us to see how the value added flows along this Global Value Chain.

@@

@@

\Cref{tab:wwz} shows the results for the example data. The first column lists exporter, exporting industry, and direct importer. Note that the value added is domestic but not necessarily created in the exporting industry. When exporter and importer are identical, the values are zero since there are no exports. The first row lists the 16 components of bilateral exports at the sector level and three checksums.

The first eight components relate to domestic value added of the exporting country contained in the sectoral exports of the exporting industry to the direct importer. For instance, the first non-zero element in \cref{tab:wwz} refers to $DVA\_FIN$ or domestic value added in final good exports. It shows that there are 5.47 units of domestic value added in the exports of final goods from Argentina's Agriculture industry to Turkey. In the same row the third term,  $DVA\_INTrexI1$, is slightly more complicated. As mentioned above it gives the amount of domestic Value added in intermediate exports re-exported to third countries as intermediate goods to produce domestic final goods. In our example this means that there are 1.14 units of domestic value added in the intermediate exports of Argentina's Agriculture industry to Turkey that are re-exported by Turkey as intermediates to a third country which produces final goods with it. Terms six to eight concern domestic value added that eventually returns home. $RDV\_FIN2$ reveals for example that there are 0.35 units of domestic value added in the intermediate exports of Argentina's Agriculture industry to Turkey that Turkey re-exports as intermediates to Argentina for the latter's final good production.
